\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics.tex
Link searches

    ``{\tt new csc courses}'' 
    & The word ``{\tt courses}'' (somewhat common with advanced query types) \\ \hline

@@

    ``{\tt MTH 2*}'' \newline ``{\tt csc 2xx}''
    & Using ``{\tt *}'' instead of an omission (e.g. ``{\tt MTH 2}'' would work) \\ \hline

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/exports}

@@

  \caption{Etc}
  \label{fig:linksearches}
\end{figure}

Success, used!

>>>>

    ``{\tt new csc courses}'' 
    & The word ``{\tt courses}'' stimies the query here (somewhat common with advanced query types) \\ \hline

@@

    ``{\tt MTH 2*}'' \newline ``{\tt csc 2xx}''
    & Using ``{\tt *}'' or ``{\tt x}'' instead of an omission (e.g. searching ``{\tt MTH 2}'' would work for this purpose) \\ \hline

@@

\begin{figure}
  \centering
  \includegraphics[width=12cm]{images/graph/exports}

@@

  \caption{Different types of ``link-search'' clicks over time, with manual instructor search included for comparison with clicking on an instructor's name}
  \label{fig:linksearches}
\end{figure}

Figure \ref{fig:linksearches} shows the amount of clicks on the Wikipedia-style embedded links throughout Skedge (instructor names to see other courses they are teaching, and prerequisite and crosslist course mentions to search those courses).

The number of manual instructor searches are also included in the graph for comparison with clicking on an instructor's name. As can be seen, clicking on an instructor's linked name is vastly more usable than searching it manually, as well as possibly offering different functionality (e.g. in the course browsing paradigm). Either way, usage of ``link-searches'' shows that they fulfill a need lacking in CDCS.
